Flaring star-planet interactions in star-planet systems in Kepler and TESS

### 2023-05-12 src/tex/ms.tex
[showyourwork] overleaf sync

We collect the planetary and stellar masses from the literature~(Table~\ref{tab:tidal}). For missing planetary masses, the radii were known, so used the mass-radius relations implemented in \texttt{forecaster}~\citep{chen2017probabilistic}. GJ 3323, GJ 674 and GJ 3082 were also missing stellar mass estimates, which we obtained from the \citep{mann2015how, mann2016erratum} relations between absolute Ks magnitude~\citep{skrutskie2006two} and stellar mass for M dwarfs using the distances from \citet{bailer-jones2021estimating}. We list the masses in Table~\ref{tab:tidal}. For Kepler-42 b, we used  $M_p=0.1-2.06M_\oplus$ that covers pure rock to pure iron compositions in \citet{muirhead2012characterizing}.

>>>>

We collect the planetary and stellar masses from the literature~(Table~\ref{tab:tidal}). For missing planetary masses, the radii were known, so used the mass-radius relations implemented in \texttt{forecaster}~\citep{chen2017probabilistic}. GJ 3323, GJ 674 and GJ 3082 were also missing stellar mass estimates, which we obtained from the \citep{mann2015how, mann2016erratum} relations between absolute Ks magnitude~\citep{skrutskie2006two} and stellar mass for M dwarfs using the distances from \citet{bailer-jones2021estimating}. We list the masses in Table~\ref{tab:tidal}. For Kepler-42 b, we used  $M_p=0.1-2.06M_\oplus$ that covers pure rock to pure iron compositions in \citet{muirhead2012characterizing}, and adopted the logarithmic mean for our estimate. Kepler-1558 c has a similar radius to Kepler-42 b, i.e., most likely a bare core planet, so we proceeded analogously to estimate its mass.
